%!TEX TS-program = xelatex
\documentclass[hidelinks,a4paper]{cv}

\usepackage{fontawesome}
\providecommand\faSkype{{\FA\symbol{"F17E}}}

\begin{document}
\header{Denys}{Potapov}
       {senior python developer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{contact}
     +38~050~330-20-57
     \faLinkedin~ \href{https://www.linkedin.com/in/denyspotapov}{denyspotapov}
     \href{mailto:denys.potapov@gmail.com}{denys.potapov@gmail.com}
  \section{python skills}
    OpenCV, numpy, pandas,
    pytest, Django
  \section{cloud expirience}
    GCP, AWS, basic Azure
  \section{other skills}
    basic Jenkins, php, go
  \section{languages}
    bilingual Ukrainian/Russian
    intermediate English
    basic German
\end{aside}

\section{profile}
I am a developer with over 12 years experience working on a variety of projects from conception to delivery. I am confident in a wide range of technologies, now focused on data processing with python. My approach is methodical but creative. I am comfortable working either independently or as part of a team.
\section{education}

\begin{entrylist}
  \entry
    {2002–2008}
    {M.Sc. degree in Computer Science}
    {NTUU 'KPI'}
    {Specialization in computer systems and robotics}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {2021-present}
    {Virtasant}
    {senior python developer}
    {Virtasant developing a SaaS solution to otimize cloud spending for clients. I'm a part of team of 3 person to port the exisitng solution for AWS to support new clouds (currentlly GCP, Axure in future).}
  \entry
    {2018—2021}
    {freelancer}
    {development}
    {Top Rated freelancer at Upwork.com. \href{https://www.upwork.com/freelancers/~019390ff2ea4f4d883}{\underline{Profile link}}. Sucessfully finished more than 60 projects in various tech (mainly python, but also JS, PHP, embedded C). Most of projects were data processing with python, including video and image processing.}
  \entry 
    {2012—2015}
    {barzo.com.ua}
    {CTO}
    {Creating and launching a start-up company. Developing from the ground e-commerce platform (PHP, MySql, HTML, SCSS). Working with and managing team of 3 freelancers.
    }
  \entry
    {2012—2018}
    {Qport}
    {project manager}
    {
    Creating a large network of digital signage systems (biggest project with 8000 screens).
    Integrating ERP system in retail stores (15 stores).
    }
  \entry
    {2009—2012}
    {Qport}
    {developer}
    {
    Developing interactive screens software (python). 
    Developing an ERP system for retail stores (1c ERP).
    }
  \entry
    {2008—2009} 
    {Physics-technological institute}
    {Leading engineer}
    {Development and integration of foundry process modeling system (Object Pascal) for perspective developments department institute of metals and alloys of the National academy of science of Ukraine}
  \entry
    {2005—2007}
    {Proling Office}
    {developer}
    {Development of machine translation system ProlingOffice (C\#) and it's online version (ASP.NET)}
\end{entrylist}

\newpage{}

\section{awards}

\begin{entrylist}
  \entry
   {June 2016}
   {Ukraine Dev Challenge}
   {3\textsuperscript{rd} place}
   {JS Front-end developer}
  \entry  
   {November 2015}
   {EU Web Challenge}
   {1\textsuperscript{st} place}
   {Back end development}
  \entry  
   {}
   {Codingame oDesk Contest}
   {5\textsuperscript{th} place}
   {python developers}
\end{entrylist}

\section{skills}
\begin{entrylist}
  \entry
   {advanced}
   {Python}
   {~}
   {
   \begin{itemize}
      \item Data processing with pandas, numpy;
      \item Image and video processing with OpenCV;
      \item Unit and integration testing;
      \item Full stack web apps with Django.
    \end{itemize}
   }
  \entry
   {intermediate}
   {front end development}
   {~}
   {JavaScript, AngularJs, HTML, CSS (SCSS)}
  \entry
   {basic}
   {php, go, c++}
   {~}
   {~}
\end{entrylist}

\section{languages}
\begin{entrylist}
  \entry
   {native}
   {Russian/Ukrainian}
   {~}
   {~}
  \entry
   {intermediate}
   {English}
   {conversationally fluent}
   {~}
  \entry
   {basic}
   {German}
   {basic words and phrases only}
   {~}
\end{entrylist}

\section{community}
\begin{entrylist}
   \entry
    {blogging}
    {\href{http://habrahabr.ru/users/patapsmile/}{habrahabr.ru}}
    {~}
    {Top-100 author in biggest Russian-speaking IT community}
   \entry
    {speaking}
    {IT conferences}
    {~}
    {Taking part in local IT conferences as visor and speaker. 
    ('Object Calisthenics in php' at WebCamp Developer Day on \href{https://www.youtube.com/watch?v=jVPtLG7q8OQ}{youtube}). 
    }
   \entry
    {open source}
    {PHP password generator library}
    {~}
    {Library has 24 stars on \href{https://github.com/denys-potapov/password-generator}{github} and more then 30 download on \href{https://packagist.org/packages/barzo/password-generator}{packagist}
    }
\end{entrylist}


\section{interests}
\begin{entrylist}
   \entry
    {volunteer}
    {Running a code club}
    {~}
    {\href{https://www.codeclub.org.uk/}{Code-club in Kyiv} is a part of network of volunteer-led after school coding clubs for children aged 9-11}
   \entry
    {running}
    {~}
    {~}
    {~}
\end{entrylist}

\end{document}